Providing better confidentiality and authentication on the Internet using Namecoin and MinimaLT

### 2013-12-23 paper.tex
Tack citation

TACK is a proposal by Moxie Marlinkspike and Trevor Perrin, it's a way to 'pin' TLS servers to the correct public key even when a Certificate Authority is telling you differently. Although this is a promising proposition, it doesn't protect against an attacker that has a long-term MITM capability since pins are set on the first connections and do expire after some time.

>>>>

TACK is a proposal by Moxie Marlinkspike and Trevor Perrin, it's a way to 'pin' TLS servers to the correct public key even when a Certificate Authority is telling you differently. Although this is a promising proposition, it doesn't protect against an attacker that has a long-term MITM capability since pins are set on the first connections and do expire after some time.\cite{tackMITM}
